The Importance of Affective States in Privacy Calculus

### 2021-05-03 submission.tex
quant discussion

There is a strong positive correlation betwen \emph{how an individual feels when
they reuse an old password, and how they feel if most of their accounts used the
same password}. The gamma correlation value of .733 is significant (p<.001,***).
The null hypothesis can be ruled out (Chi-Square p<.01,**).
\section{Discussion}
\subsection{Ad Tracking}
\textbf{TODO}
The inability to rule out the null hypothesis is likely due to the small sample
size of 34 respondents who were asked these questions.

>>>>

There is a strong positive correlation betwen \emph{how an individual feels when
they reuse an old password, and how they feel if most of their accounts used the
same password}. The gamma correlation value of .733 is significant (p<.001,***).
The null hypothesis can be ruled out (Chi-Square p<.01,**).

\section{Discussion}
\subsection{Privacy Habits and Affectives States}
Strong correlations exist between how people feel and their privacy related
habits. Intuitively, privacy related behavior and habits are comparable to
housekeeping insomuch as they are not immediately sources of great happiness,
but they offer long term benefits. Individuals who feel good when they engage in
privacy conscious behavior tend to practice such behavior more frequently.
\emph{It is unclear whether the habit itself causes the individual to experience
more positive affective states, or whether it is the affective states that
determine whether an individual is likely to form such a habit or not.}

% Should this go into a Further Research section?
In future research, a behavioral study leveraging regression discontinuity
design can provide insight as to the directionality of the relationship between
privacy habits/behavior and affective states.

For nearly all the relationships that were analyzed, it is not possible to rule
out the null hypothesis due to the survey's insufficient sample size.
